### 2017-01-28 thesis/results/results.tex
Finished FM metagene section (but very rough)

Lastly, the transformation matrix was applied to Print's data.

\\

@@

\noindent

>>>>

Lastly, the transformation matrix was applied to Print's data (\cref{fig:fmmetaboxcris1,fig:fmmetacris1}).
Again, FM's obesity metagene scores reflected the gene expression of the samples, did not significantly associate with sample \gls{bmi}/\gls{bmi} status.
\\

@@

\noindent
These results showed that FM's obesity associated metagene was not transferable to other cancer data sets, similar to Creighton's obesity associated metagene.
This meant that neither Creighton's nor FM's obesity associate metagenes may be too specific to the orignial data set in which the signature was identified in.
Furthermore, it may be possible that these obesity associated metagenes may not be related to obesity, but another clinical variable which may be closely related to \gls{bmi}.
